%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Sentiment Analysis on Amazon India Reviews} \href{https://github.com/pranavagrawal321/Sentiment-Analysis-on-Amazon-Reviews}{\faShare}} {}
    \resumeItemListStart
        \resumeItem {Spearheaded the implementation of advanced Sentiment Analysis algorithms to analyze and classify customer reviews across multiple product categories on Amazon India.}
        \resumeItem{Scrapped data for the dataset using Selenium and HTML Parser.}
        \resumeItem{Trained and evaluated various machine learning models to accurately classify sentiment in textual data.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Book Recommender System} \href{https://github.com/pranavagrawal321/Book-Recommender-System}{\faShare}} {}
    \resumeItemListStart
        \resumeItem {Developed a recommender system for books to recognise similar books.}
        \resumeItem{Used book title to calculate similarity.}
        \resumeItem{Used Cosine similarity to calculate and predict the similarity score for books.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Profit Dashboard using Tableau} \href{https://github.com/pranavagrawal321/Profit-dashboard-using-Tableau}{\faShare}} {}
    \resumeItemListStart
        \resumeItem {Developed a dashboard to display insights of a business.}
        \resumeItem{Used the inbuilt sales dataset.}
        \resumeItem{Displayed various metrics using various KPIs present in the data.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{T20 Cricket World Cup 2022 Dataset} \href{https://github.com/pranavagrawal321/T20-World-Cup-Dataset}{\faShare}} {}
    \resumeItemListStart
        \resumeItem {Developed a dashboard to display insights of a business.}
        \resumeItem{Used the inbuilt sales dataset.}
        \resumeItem{Displayed various metrices using various KPIs present in the data.}
    \resumeItemListEnd

\resumeSubHeadingListEnd